
---
title: "Peer Assessment 1 - Reproducible Research"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Loading and preprocessing the data:
```{r}
setwd("activity")
data <- read.csv("activity.csv")
data$date <- as.Date(data$date)
ag <- aggregate(steps ~ date, data, sum)
```

## What is mean total number of steps taken per day?

###Histogram of the total number of steps taken each day
```{r}
hist(ag$steps, xlab="Steps", main="Steps")
```
###Mean Steps:
```{r}
mean(ag$steps)
```
###Median Steps:
```{r}
median(ag$steps)
```

## What is the average daily activity pattern?
```{r}
ag <- aggregate(steps ~ interval, data, sum)
plot(x=ag$interval, y=ag$steps, type="l", xlab="interval", ylab="steps", main="Steps over Interval")
```
###Max Steps in 5-Min Interval:
```{r}
ag[which(ag$steps==max(ag$steps)), ]
```

## Imputing missing values
###Total Number of NAs
```{r}
sum(is.na(data))
```
Fill NAs with the median for that 5 minute interval
```{r}
data$steps[is.na(data$steps)] <- with(data, ave(steps, interval, FUN = function(x) median(x, na.rm=TRUE)))[is.na(data$steps)]
ag <- aggregate(steps ~ date, data, sum)
```

###Histogram Steps
```{r}
hist(ag$steps, xlab="Steps", main="Steps")
```
###Mean Steps:
```{r}
mean(ag$steps)
```
###Median Steps:
```{r}
median(ag$steps)
```

## Are there differences in activity patterns between weekdays and weekends?

###Add weekday factor distinction to data and plot
```{r}
library(dplyr)
library(lattice)
data$weekday <- weekdays(data$date) %in% c("Saturday", "Sunday")
data$weekday <- as.factor(data$weekday)
levels(data$weekday) = c("Weekday", "Weekend")

ag <- data %>% select(-(date)) %>% group_by(weekday, interval) %>% summarise_each(funs(mean))

xyplot(steps ~ interval | weekday, data, type = "l", layout = c(1,2))
```

